Network Data Collection for Artifical Intelligence

### 2020-02-28 paper2/paper2.tex
Fix errors

\begin{figure}[htbp]
\centerline{\includegraphics[scale=0.25]{docker_vm.png}}
\caption{Virtual machines vs. Containers \cite{b8}}
\label{docker-vm}
\end{figure}

Hypervisors like VirtualBox or VMware provide the possibility to setup full virtual computers on a physical host where Docker containers are encapsuled sandboxes on an existing operating system like illustrated in Fig.~\ref{docker-vm}. It is clear that containers are more resource efficent but in virtual machines the systems are better isolated. In our case we could use both solutions because the network simulators are also capable to run in Docker containers. If we focus on resource efficency and scalability also Kubernetes comes in our minds which is an orchestrator for deploying Docker containers on multiple nodes but it is a more complex configuration overhead and needs certain amount of hardware to unfold its potential also for simple scenarios. Because we want an affordable solutions which can be used in most of the cases also on our computers with some exceptions, we decided to use a tool which can create virtual machines as well as Docker containers to be ready for the future. Regarding the corner cases servers or a Kubernetes cluster could be rented temporarily on cloud platforms to support high-load scenarios e.g. big denial-of-service attacks.

A popular solution to bootstrap development environments in virtual machines is called Vagrant which provides lightweight base images and an interface to automate the configuration of the virtual machines. Moreover it can be connected to provisioning tools to further configure host systems. Vagrant supports VirtualBox or VMware but also Docker and can be extended to support cloud services like AWS or even to install a whole Kubernetes cluster. It gives us the power to start with simple configurations and scale them up to more sophisticated ones using containerization and complex orchestrators. \cite{b9}

This means we are ready to create system environments on our host or in the cloud and install base systems on them. The next section focuses on the automated setup of the network simulator, recorder and data extractor within virtual machines or Docker containers as well as the configuration of network topologies based on the selected scenarios and parameters to produce, record and extract network traffic for further processing in neuronal networks to improve their strike rate.

@@

Fig.~\ref{docker-vm} shows a schematic overview of the simulation workflow. The input parameters are the type of scenario(s) and the respective settings which deploys hosts including the base systems and the simulators applying the network topologies. Moreover the network recorder and data extractor will be deployed to gather the network traffic and extract the features to create data sets which could be collected in a central database.

>>>>

\begin{figure}[htbp]
\centerline{\includegraphics[scale=0.5]{docker_vm.png}}
\caption{Virtual machines vs. Containers \cite{b8}}
\label{docker-vm}
\end{figure}

Hypervisors like VirtualBox or VMware provide the possibility to set up full virtual computers on a physical host (see Fig.~\ref{docker-vm}a) while Docker containers are encapsuled sandboxes on an existing operating system (see Fig.~\ref{docker-vm}b). It is clear that containers are more resource efficent but in virtual machines the systems are better isolated. In our case we could use both solutions because the network simulators are also capable to run in Docker containers. If we focus on resource efficency and scalability also Kubernetes comes in our minds which is an orchestrator for deploying Docker containers on multiple nodes but it is a more complex configuration overhead and needs certain amount of hardware to unfold its potential also for simple scenarios. Because we want an affordable solution which can be used in most of the cases also on our computers with some exceptions, we could use a tool which can create virtual machines as well as Docker containers to be ready for the future. Regarding the corner cases servers or a Kubernetes cluster could be rented temporarily on cloud platforms like AWS to support high-load scenarios e.g. big denial-of-service attacks. \cite{b8}

A popular solution to bootstrap development environments in virtual machines is called Vagrant which provides lightweight base images and an interface to automate the configuration of the virtual machines. Moreover it can be connected to provisioning tools to further configure host systems. Vagrant supports VirtualBox or VMware but also Docker and can be extended to support cloud services like AWS or even to install a whole Kubernetes cluster. It gives us the power to start with simple configurations and scale them up to more sophisticated ones using containerization and complex orchestrators. \cite{b9} \cite{b10}

This means we would be ready to create system environments on our host or in the cloud and install base systems on them. The next section focuses on the automated setup of the network simulator, recorder and data extractor within virtual machines or Docker containers as well as the configuration of network topologies based on the selected scenarios and parameters to produce, record and extract network traffic for further processing in neuronal networks to improve their strike rate.

@@

Fig.~\ref{design-flow} shows a possible simulation workflow. The input parameters are the type of scenario(s) and the respective settings which deploys hosts including the base systems and the simulators applying the network topologies. Moreover the network recorder and data extractor could be deployed to gather the network traffic and extract the features to create data sets which could be collected in a central database.
